\subsection{Architecture}

This chapter will describe in detail how our application
is build, how it works and what we use to achieve
concurrency.

On a higher level our application is devided into two
distinct parts, the Executor ($E$) and the Worker ($W$).

$E$ is the part of our application that is doing the
training and testing of our agent, while  $W$ generates
training data which is sent via the RabbitMQ to $E$ so $E$
can train the agent with this data. After training $E$
sends the agent to $W$ so $W$ can generate new training
data with the updated agent.

This iteration is continued until the agent is able to
solve the Gym environment (cmp. \ref{s_openai_gym}).

\input{app/arch/network}

\input{app/arch/executor}

\input{app/arch/worker}

\subsubsection{Queues and Exchanges}

Now, this chapter will go more into detail on how we
utilize the RabbitMQ.

First, there are two concepts we used for communication
with the RabbitMQ called queues and exchanges.

\begin{itemize}[label={}]

  \item \textbf{queue:}

        This concept we already discussed in chapter
        \ref{ss_mb_faa}. Now, for our project one property
        of a queue is interesting, which is "first come,
        first serve" or "FIFO" (First In, First Out), which
        means once a message is received by a listener
        (also called consumer), other listeners (consumers)
        that subscribed to this particular queue will never
        receive this message and all subscribed listeners
        are in a race condition for the next message.

        Because of this we need another concept for
        distributing certain messages (e.g. sending our
        agent to each Worker, since every Worker should use
        a current version of the agent wich would not be
        possible if a Executor would send the agent to a
        queue, because then only one would receive the new
        agent instead of all Workers).
        \index{RabbitMQ!queue}

  \item \textbf{exchange:}

        For the above mentioned szenario we need a
        different message distribution called
        publish/subscribe.

        Publish/subscribe message distribution can be
        achieved with an exchange provided by the RabbitMQ.

        In this szenario the Executor would by the
        publisher while the Workers would be the
        subscribers. For every listener (subscriber)
        RabbitMQ generates a new queue and redistributes
        every message published to the exchange to the
        queues.

        For this redistribution or routing are some methods
        available. We only used the method called fanout,
        which generates a copy of every published message
        for each listener (consumer) receiving on an
        exchange.
        \index{RabbitMQ!exchange}

\end{itemize}

\input{diagrams/queue_exchange}

The queues and exchanges we used in our project:

\begin{itemize}[label={}]

  \item \textbf{meta\_queue:}

        Queue the meta process of the Executor(s) is/are
        listening to. This queue is used by Workers to
        ask for the environment and for sending the
        protocol once the agent succeeded.
        \index{Application!meta\_queue}

  \item \textbf{meta\_exchange:}

        Corresponds to meta\_queue. The Executor(s) is/are
        answering with the environment on this exchange.
        \index{Application!meta\_exchange}

  \item \textbf{data\_queue:}

        Queue used by the Workers to send their generated
        training data to the Executor(s).
        \index{Application!data\_queue}

  \item \textbf{model\_exchange:}

        Exchange the Executor(s) use(s) for sending the new
        agent to each Worker or, if the agent succeeded,
        for sending a message telling each Worker to send
        their protocols and shut down afterwards.
        \index{Application!model\_exchange}

\end{itemize}

